Group Signatures Meet Anonymous Credentials: Or, How to Build Privacy Preserving Identities with Accountability

### 2022-02-19 prism-backend/research/gsac/uas-model.tex
Refined oracles. Completed correctness definition (v1). Working on anoymity.

\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\LangIss)$.] Given global system
  parameters \parm, and the language \LangIss defining the NP relation for
  issuance, an issuer runs this function to generate its issuing key pair.
  Hereafter, we assume that the public part \ipk is added to the group public
  key \gpk.
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\LangIns)$.] Given global system
  parameters \parm, and the language \LangIns defining the NP relaton for
  inspection, an inspector runs this function to generate its inspecting key
  pair. It returns the inspector's key pair. Hereafter, we assume that the
  public part \opk is added to the group public key \gpk.

@@

  \Obtain(\usk,\uattrs,\dattrs,\ldblbrace (gpk_i,\cred_i,\tuattrs_i,\tdattrs_i)\rdblbrace_{i \in \Issuers}),
  \Issue(\isk,\upk,\dattrs,\ldblbrace (\gpk_i,\tdattrs_i)\rdblbrace_{i \in \Issuers})

@@

@@

    \caption{Detailed oracles available in our model (1/2). Oracles for
      generating users, issuers, and inspectors.\\
      \doubt{Do we need to specify the functions in the GEN Oracles? They do
        not seem necessary in \SIGN/\CHALb/\INSPECT. Should they? Maybe there
        is something wrong here... Maybe they are needed in the games...}}
    \label{fig:oracles1}
  \end{figure*}
}

@@

        \procedure{$\OBTISS(\cid,\uid,\gid,\uattrs,\dattrs,
          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\          
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot:
          \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\PRVUK[\uid],\uattrs,\dattrs,\ldblbrace (\GK[\sgid],
          \CRED[\scid],\tuattrs,\tdattrs) \rdblbrace), \\
          \pcind \pcind \pcind \pcind \pcind \pcind
          \Issue(\PRVIK[\gid],\PUBUK[\uid],\ldblbrace (\GK[\sgid],\tdattrs)
          \rdblbrace ) \rangle \\
          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid,\uattrs,\dattrs) \\
          \pcreturn \top \\
        }

        \procedure{$\SIGN(\msg,\uid,\uattrs,\dattrs,
          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace )$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \cred \gets \CRED[\cid] \\
          \sig \gets \Sign(\PRVUK[\uid],\msg,\uattrs,\dattrs,
          \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\sig,\msg,\scid,\uattrs,\dattrs,\sgid) \rbrace \\
          \pcreturn \sig \\
        }

        \procedure{$\CHALb(\msg,
          (\uid_{0,1},\uattrs_{0,1},\dattrs_{0,1},\ldblbrace (\sgid,\cscid_{0,1},\tuattrs_{0,1},\tdattrs_{0,1}) \rdblbrace))$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pccomment{Note: since both \uid's need to be honest, we must have
            all the}\\
          \pccomment{undisclosed attributes in the \ATTR lists.} \\
          \dattrs' \gets \DATTR[\cscid_0] \cap \DATTR[\cscid_1] \\
          \uattrs' \gets \UATTR[\cscid_0] \cap \UATTR[\cscid_1] \\
          \pcif (\dattrs_0 \cap \dattrs_1) \nsubseteq \dattrs':
          \pcreturn \bot \\
          \pcif (\uattrs_0 \cap \uattrs_1) \nsubseteq \uattrs':          
          \pcreturn \bot \\
          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\uattrs_b,\dattrs_b,
          \ldblbrace (\GK[\sgid],\CRED[\scid_b],\tuattrs_b,\tdattrs_b) \rdblbrace) \\
          \CSIG \gets \CSIG \cup
          \lbrace (\csig,\msg,\scid_b,\uattrs_b,\dattrs_b,\sgid) \rbrace \\
          \pcreturn \csig
        }

@@

\paragraph{Correctness.} %
Correctness of \GSAC schemes is formalized through the experiment in
\figref{fig:exp-gsac-corr}. It states that a signature for some message \msg,
revealing attributes \dattrs, which was honestly produced though a credential
that was obtained by an honest user interacting with an honest issuer, with a
set of attributes \attrs such that $\dattrs \subseteq \attrs$, must be accepted
by \Verify. Moreover, an honestly produced correctness proof of opening for such
signature, revealing the public key pair of the user, must also be accepted by
\Judge.

\begin{figure}[htp!]
  \procedure{$\ExpCorrect(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
     \gpk \gets (\ipk,\opk) \\
    (\cid,\dattrs,\msg) \gets \adv^{\HUGEN,\OBTISS}(\gpk) \\
    \pcif \dattrs \nsubseteq \ATTR[\cid] :
    \pcreturn \bot \\
    \sig \gets \Sign(\gpk,\PRVUK[\OWNR[\cid]],\CRED[\cid],\dattrs,\msg) \\
    (\upk,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\dattrs,\msg) \\
    \pcif \Verify(\gpk, \sig, \dattrs,\msg) = 0 \lor
    \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 0:
    \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Correctness experiment for \GSAC schemes.}
  \label{fig:exp-gsac-corr}
\end{figure}

@@

\paragraph{Anonymity.} %
In group signatures, anonymity captures that no adversary must be able to learn,
from any group signature, anything about its signer. In anonymous credentials,
it requires that no adversary should learn anything about the holder of a
credential that has been successfully shown, beyond that he owns a credential
containing the revealed attributes. In both GS and AC, it is also typically
required that
multiple signatures/presentations by the users are unlinkable. The approach to
formally state this property is in both cases frequently the same: the adversary
picks two (honest) users (or credentials in the AC case), the game randomly
chooses one of them, and lets the adversary request challenge
signatures/presentations from it. The adversary wins if it succeeds in guessing
which was the chosen user/credential better than guessing at random. In group
signatures, the game must also restrict the adversary from opening challenge
signatures. In anonymous credentials, the game must further constraint the
adversary to output credentials that have some common subset of attributes, and
to use that common subset to request the challenge presentations. Here, we need
to take into account both. Furthermore, a key difference with group signatures
is that the game requires the adversary to output credential identifiers, rather
than user identifiers. Specifically, this means that the adversary may actually
output two credentials that belong to the same user. Therefore, in some sense,
the anonymity we get is more general than that of group signatures. The formal
specification of the anonymity game is given in \figref{fig:exp-gsac-anonb}.
%
Similarly, this notion of anonymity is also stronger than the notion of
anonymity in both group signatures and anonymous credentials, in the sense
that calls to the \OPEN oracle reveal the public key and credential of the users
that (via the \SIGN and \CHALb oracles) create the signatures that the adversary
sees. Therefore, all security relies \emph{only} on the user secret key.

\begin{figure}[htp!]
  \procedure{$\ExpAnonb(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
     \gpk \gets (\ipk,\opk) \\
     (\cid_0,\cid_1,\status) \gets
     \adv^{\HUGEN,\CUGEN,\OBTAIN,\SIGN,\OPEN}(\choose,\gpk,\isk) \\
     b^* \gets
     \adv^{\HUGEN,\CUGEN,\OBTAIN,\SIGN,\OPEN,\CHALb}(\guess,\gpk,\isk,\status) \\
     \pcreturn b^*
  }
  \caption{Anonymity experiment for \GSAC schemes.}
  \label{fig:exp-gsac-anonb}
\end{figure}

@@

\paragraph{Traceability.} %
Traceability is one of the unforgeability-related properties in group
signatures. It captures that any signature accepted by \Verify needs to open
to one of the users that joined the group. While there is no traceability notion
in anonymous credentials, it is natural to map it to their unforgeability
property; if only because both require the issuer to be honest. Unforgeability
in anonymous credentials typically ensures that no adversary can get a verifier
to accept a credential presentation requiring a set of attributes that is not
contained in one of the credentials controlled by the adversary.
%
Our notion of traceability for \GSAC combines both requirements. It assumes an
honest issuer, as otherwise the adversary can create untraceable credentials at
will. The game then lets the adversary add honest and corrupt users, create
honest signatures, and open them. The adversary wins if, after this interaction,
is able to produce a $(\sig,\dattrs,\msg)$ tuple that is accepted by \Verify,
but either cannot be opened, it can be opened by the proof is rejected by
\Judge, or even though it is accepted by \Judge, there was no issued credential
(honest or not) that contained the set of attributes \dattrs. We formally
define traceability in the \ExpTrace experiment in \figref{fig:exp-gsac-trace}.

@@

\paragraph{Non-frameability.} %
Non-frameability variants are a core unforgeability-type property in group
signatures. However, no
similar property is modeled for anonymous credentials (\todo{see the discussion
  in \secref{sec:introduction} for further detail}). It is a quite strong
property, as it must be ensured even in the presence of dishonest issuer and
opener. Intuitively, it prevents the adversary from creating a signature that
frames an honest user. Depending on the inspection capabilities of the scheme,
this framing could be done in different ways; i.e., by convincing third parties
that signatures by different (possibly corrupt) users are linked, or directly
by having open proofs output the identity of a user who did not create the
signature being opened.
%
In \GSAC schemes, in order for a user to be framed, the adversary first needs to
create a $(\sig,\dattrs,\msg,\upk,\cred,\oproof)$ such that the signature,
attributes, and message are accepted by \Verify, and which, along with the user
public key, credential, and open correctness proof, are accepted by \Judge.
Then, the adversary wins the game if the owner of the credential is honest, but
the signature was not produced via the \SIGN oracle, or if the public key output
by the adversary does not match the public key associated to the credential
owner.
%
Note that, as in anonymity, this notion of non-frameability is even stronger
to that of group signatures, since our \Open function returns both the public
key and the credential that were used to create the signature.

>>>>

\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. Hereafter, we assume that the
  public part \ipk is added to the group public key \gpk, as well as \fissue.
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\feval,\finsp)$.] Given global system
  parameters \parm, and two functions \feval and \finsp, an inspector runs
  \OKeyGen to generate its inspecting key pair. The function \feval defines
  requirements that signed message-signature pairs must meet. The function
  \finsp defines the type of utility that will be extractable from those pairs
  that do not meet \feval. Hereafter, we assume that the public part \opk is
  added to the group public key \gpk, along with \feval and \finsp.

@@

  \Obtain(\usk,\uattrs,\dattrs,
  \ldblbrace (gpk_i,\cred_i,\tuattrs_i,\tdattrs_i)\rdblbrace_{i \in \Issuers}),
  \Issue(\isk,\upk,\dattrs,
  \ldblbrace (\gpk_i,\tdattrs_i)\rdblbrace_{i \in \Issuers})

@@

\paragraph{Issuance, evaluation, and inspection private functions.} %
We emphasize that, both in our syntax definition, as well as on the following
modelling, we make use of three different and abstract functions: \fissue,
\feval and \finsp. The three functions are run by users (maybe, on user-private
data) as part of different algorithms in an \UAS scheme. In all cases, the
user has to prove correctness of their computation. We introduce them next,
\todo{and will give concrete examples in \secref{sec:uac-instantiation}.}

\todo{Domains (attributes, messages, etc.) are not correctly defined here. But
  for now, just leave it as is to at least convey the idea. Also, this needs
  refinement in general: what properties (if any) do these functions need to
  meet in order to be meaningful?}
\begin{description}
\item[$\fissue: (\uattrs,\dattrs) \rightarrow 0/1$.] Governs what customized
  conditions an issuer requires in order to issue credentials, when receiving
  a request from a user with a set of disclosed attributes \dattrs, and
  undisclosed attributes \uattrs (which need to be kept private from the
  issuer). \fissue returns 1 to accept a request, 0 to reject it.  
\item[$\feval: (\msg,\sig) \rightarrow 0/1$.] Governs customized conditions upon
  which a verifier should accept (1) or reject (0) a given message-signature
  pair.
\item[$\finsp: (\upk,\scred) \rightarrow \bin^*$.] Defines what utility value,
  derived from the user's public key and credentials, should be extractable by
  the group inspector.
\end{description}

@@

    \caption{Detailed oracles available in our model (1/2). Oracles for
      generating key material for users, issuers, and inspectors.\\
      \doubt{Do we need to specify the functions in the GEN Oracles? They do
        not seem necessary in \SIGN/\CHALb/\INSPECT. Should they? Maybe there
        is something wrong here... Maybe they are needed in the games...}}
    \label{fig:oracles1}
  \end{figure*}
}

@@

        \procedure{$\OBTISS(\cid,\uid,\gid,\uattrs,\dattrs,
          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\          
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot:
          \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\PRVUK[\uid],\uattrs,\dattrs,\\
          \hspace*{75pt} \ldblbrace (\GK[\sgid],
          \CRED[\scid],\tuattrs,\tdattrs) \rdblbrace), \\
          \hspace*{60pt} \Issue(\PRVIK[\gid],\PUBUK[\uid],
          \ldblbrace (\GK[\sgid],\tdattrs)
          \rdblbrace ) \rangle \\
          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid,\uattrs,\dattrs) \\
          \pcreturn \top \\
        }

        \procedure{$\SIGN(\msg,\uid,\uattrs,\dattrs,
          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace )$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \cred \gets \CRED[\cid] \\
          \sig \gets \Sign(\PRVUK[\uid],\msg,\uattrs,\dattrs, \\
          \hspace*{42pt}
          \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\sig,\msg,\scid,\uattrs,\dattrs,\sgid) \rbrace \\
          \pcreturn \sig \\
        }

        \procedure{$\CHALb(\msg,
          (\uid_{0,1},\uattrs_{0,1},\dattrs_{0,1},\ldblbrace (\sgid,\cscid_{0,1},\tuattrs_{0,1},\tdattrs_{0,1}) \rdblbrace))$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pccomment{Note: since both \uid's need to be honest, we must have
            all the}\\
          \pccomment{undisclosed attributes in the \ATTR lists.} \\
          \dattrs' \gets \DATTR[\cscid_0] \cap \DATTR[\cscid_1] \\
          \uattrs' \gets \UATTR[\cscid_0] \cap \UATTR[\cscid_1] \\
          \pcif (\dattrs_0 \cap \dattrs_1) \nsubseteq \dattrs':
          \pcreturn \bot \\
          \pcif (\uattrs_0 \cap \uattrs_1) \nsubseteq \uattrs':          
          \pcreturn \bot \\
          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\uattrs_b,\dattrs_b, \\
          \hspace*{42pt}
          \ldblbrace (\GK[\sgid],\CRED[\scid_b],\tuattrs_b,\tdattrs_b) \rdblbrace) \\
          \CSIG \gets \CSIG \cup
          \lbrace (\csig,\msg,\scid_b,\uattrs_b,\dattrs_b,\sgid) \rbrace \\
          \pcreturn \csig
        }

@@

\paragraph{Correctness.} %
Correctness of \UAS schemes is formalized through the experiment in
\figref{fig:exp-uas-corr}. It states that a signature for some message \msg,
revealing attributes \dattrs, which was honestly produced though a credential
that was obtained by an honest user interacting with an honest issuer, with a
set of attributes \attrs such that $\dattrs \subseteq \attrs$, must be accepted
by \Verify. Moreover, an honestly produced correctness proof of opening for such
signature, revealing the public key pair of the user, must also be accepted by
\Judge.

\begin{figure}[htp!]
  \procedure{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\msg,\uattrs,\dattrs,
    \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)
    \gets \adv^{\HIGEN,\HOGEN,\HUGEN,\OBTISS}(\parm) \\
    \pcif \dattrs \nsubseteq \bigcup_{\cid \in \scid} \DATTR[\cid] \lor
    \bigcup \tdattrs \nsubseteq \dattrs: \pcreturn \bot \\
    \sig \gets \Sign(\PRVUK[\uid],\msg,\uattrs,\dattrs,
    \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace ) \\
    \pccomment{Signature fails to verify} \\
    \pcif \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 0: \pcreturn 0 \\
    \pccomment{An inspector among those involved in credentials used to produce
      \sig cannot inspect it} \\
    \pcif \exists \gid \in \sgid~\st~
    \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,
    \ldblbrace \GK[\sgid] \rdblbrace) = \bot: \pcreturn 0 \\
    \pccomment{Some of the produced $(\y,\iproof)$ pairs is rejected by
      \Judge \todo{This must be conditioned on \feval = 0!}} \\
    \pcif \exists \gid \in \sgid~\st~
    (\y,\iproof) \gets \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,
    \ldblbrace \GK[\sgid] \rdblbrace) \land \\
    \pcind
    \Judge(\y,\iproof,\sig,\msg,\dattrs,\ldblbrace \GK[\sgid] \rdblbrace) = 0):
    \pcreturn 0 \\
    \textrm{Let}~(\fissue^\gid,\feval^\gid,\finsp^\gid)~\textrm{denote the
      issue, evaluation and inspection functions defined} \\
    \textrm{by each $\gid \in \sgid$} \pccomment{\todo{Come up with some
        notation for this}} \\
    \pccomment{\fissue rejects some issued credential} \\
    \pcif \exists \gid \in \sgid~\st~\fissue^\gid(\tuattrs,\tdattrs) = 0:
    \pcreturn 0 \\
    \pccomment{\feval rejects the signature-message pair} \\
    \pcif \exists \gid \in \sgid~\st~\feval^\gid(\msg,\sig) = 0: \pcreturn 0 \\
    \pccomment{\y is the wrong value according to \finsp} \\
    \pcif \exists \gid \in \sgid~\st~
    \y \neq \finsp^\gid(\PUBUK[\uid],\CRED[\scid])): \pcreturn 0 \\
    \pcreturn 1
  }
  \caption{Correctness experiment for \UAS schemes. \todo{Reorganize this.}}
  \label{fig:exp-uas-corr}
\end{figure}

@@

\paragraph{Anonymity.} %
In group signatures, anonymity captures that no adversary must be able to learn,
from any group signature, anything about its signer. In anonymous credentials,
it requires that no adversary should learn anything about the holder of a
successfully shown credential, beyond that he owns a credential attesting for
the claimed function of attributes it contains. In both GS and AC, it is also
typically required that
multiple signatures/presentations by the users are unlinkable. The approach to
formally state this property is in both cases frequently the same: the adversary
picks two (honest) users (or credentials in the AC case), the game randomly
chooses one of them, and lets the adversary request challenge
signatures/presentations from it. The adversary wins if it succeeds in guessing
which was the chosen user/credential better than guessing at random. In group
signatures, the game must also restrict the adversary from opening challenge
signatures. In anonymous credentials, the game must further constraint the
adversary to output credentials that have some common function of (a subset of)
its attributes.

In our notion of anonymity for \UAS, we need to merge the previous constraints.
Furthermore, a key difference with group signatures is that the game requires
the adversary to output credential identifiers, rather than user identifiers.
Specifically, this means that the adversary may actually output two credentials
that belong to the same user. Therefore, in some sense, the anonymity we get is
more general than that of group signatures. Moreover, in order to prevent
trivial wins by the adversary, we have to restrict that the challenge signatures
belong to a group that has been ``programmed'' with the same evaluation and
inspection functions. The formal specification of the anonymity game is given in
\figref{fig:exp-uas-anonb}.

\begin{figure}[htp!]
  \procedure{$\ExpAnonb(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\cscid_0,\cscid_1,\status) \gets
     \adv^{\lbrace\HI,\CI,\HO,\CO,\HU,\CU\rbrace\GEN,\OBTAIN,\SIGN,\INSPECT}
     (\choose,\parm) \\
     b^* \gets
     \adv^{\lbrace\HI,\CI,\HO,\CO,\HU,\CU\rbrace,\GEN,\OBTAIN,\SIGN,\INSPECT,\CHALb}
     (\guess,\status) \\
     \pcreturn b^*
  }
  \caption{Anonymity experiment for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure}

@@

\paragraph{Discussion on the generic anonymity of \UAS schemes.} %
This notion of anonymity is also more general in the sense that calls to
the \INSPECT oracle reveal an arbitrary function of the identity of the user
-- which can certainly be the identity itself, as in group signatures, ore any
other function computable from the \textcolor{red}{user public key and all of
  its credentials}. Of course, this requires to restrict the adversary to
programming equivalent inspection functions in the challenge signatures it
gets (or, more precisely, into the groups they belong to). While this could
appear as having a more restricted type of anonymity -- and indeed it could be
for some subset of inspection functions -- we point out that it is just a
generalization, as the concrete inspection function depends on the needs of
the use case where a \UAS scheme is to be integrated.

\paragraph{Traceability.} %
Traceability is one of the unforgeability-related properties in group
signatures. It captures that any signature accepted by \Verify needs to open
to one of the users that joined the group. While there is no traceability notion
in anonymous credentials, it is natural to map it to their unforgeability
property; if only because both require the issuer to be honest. Unforgeability
in anonymous credentials typically ensures that no adversary can get a verifier
to accept a credential presentation requiring a set of attributes that is not
contained in one of the credentials controlled by the adversary.
%
Our notion of traceability for \UAS...

@@

\paragraph{Non-frameability.} %
Non-frameability variants are a core unforgeability-type property in group
signatures. However, no
similar property is modeled for anonymous credentials (\todo{see the discussion
  in \secref{sec:introduction} for further detail}). It is a quite strong
property, as it must be ensured even in the presence of dishonest issuer and
opener. Intuitively, it prevents the adversary from creating a signature that
frames an honest user. Depending on the inspection capabilities of the scheme,
this framing could be done in different ways; i.e., by convincing third parties
that signatures by different (possibly corrupt) users are linked, or directly
by having open proofs output the identity of a user who did not create the
signature being opened.
%
In \UAS schemes, in order for a user to be framed...
